---
title: "Engagement_report"
author: "Group 1"
date: "10/20/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project Background 

Our project will be stored in one main folder that contains a code folder and output folder. In the main project folder, there will also be a render.R file, an RMD file with the combined report, and a make file. In the Code folder, there will be a .R file for each of the coder’s parts. In the output folder, there will be the outputs for each of the parts. See below for visual structure. 


# Project folder
Folder: CODE
  01_unique_views.R
  02_total_views.R
  03_video_length.R
Folder: OUTPUT
  Output for each coder’s part (.png, .rds etc)
Render_report.R
Combined_report.Rmd
Makefile

Finally, we will customize the report using a config file. The user will select which week they want to produce in the tables and graphs of our combined_report. Each part of the output will be customized with whatever week the user would like to view.  

```{r, include=FALSE}
configlist<-config::get()
```

# Unique views figure and graph
## Unique viewers table
```{r, unique viewers table}
table <- readRDS(
  file = here::here(paste0("output/week",configlist$numberparam,"_Unique_views_table.rds"))
)
table
```
## Unique viewers figure
```{r, Unique viewers bar plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here(paste0("output/week",configlist$numberparam,"_Unique_views_barplot.png"))
)
```

# Video Length table and graph
## video length table
```{r, video length table}
table <- readRDS(
  file = here::here(paste0("output/week",configlist$numberparam,"_video_length_table.rds"))
)
table
```
## Unique viewers figure
```{r, video length bar plot}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here(paste0("output/week",configlist$numberparam,"_video_length_plot.png"))
)
```